% Created 2018-02-12 Mon 11:12
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Monib Ahmed}
\date{\today}
\title{WORKING ON ORGANIZING NOTES}
\hypersetup{
 pdfauthor={Monib Ahmed},
 pdftitle={WORKING ON ORGANIZING NOTES},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 25.3.1 (Org mode 9.1.5)}, 
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents


\section{Overall goals:}
\label{sec:org01c4e63}
\begin{itemize}
\item Have a reference to go back to.
\item Be able to highlight the work you've done.
\item Learn and update, not everything needs to be known now.
\end{itemize}

\section{Organization:}
\label{sec:org7cdce0f}
\begin{itemize}
\item Notes Taking
\begin{itemize}
\item Structure Notes
\item Capture Notes
\item Publish Notes
\end{itemize}
\item Task Management
\begin{itemize}
\item Capture tasks Bin appropriate tasks
\item Track tasks
\end{itemize}
\end{itemize}

\section{How to get more get in the same amount of time}
\label{sec:org502d3d2}
\begin{itemize}
\item Simplify with KISS
\begin{itemize}
\item Time over money, what keeps life easier is better
\end{itemize}
\item Utilize other people's experience
\begin{itemize}
\item Talk to people, and utilize their experience
\item Augment it with your own
\end{itemize}
\item Put some feeling into it, you retain more with feeling
\begin{itemize}
\item Experience it, feel it, nurture it, live it.
\end{itemize}
\item Elimiate time wasting activities
\begin{itemize}
\item These thing keep you from doing other things.
\end{itemize}
\end{itemize}

\section{My Life Goals}
\label{sec:org5ce9a14}
\subsection{Spirituality}
\label{sec:orgebb7983}
Learn and feel connected to God, always. Remember him, and
incorporate Him into your life.
\subsection{Health}
\label{sec:orgdea2128}
Be stronger and healthier. 
\subsection{People}
\label{sec:orga1abaff}
Learn how to deal with people, and get your goals completed. Be
happier with response of people.
\subsection{Career}
\label{sec:orgb344a07}
Get to a point where you are technically satisfied, in a company
doing what you think is important.
\subsection{Music}
\label{sec:orga8943f0}
Play music live, improvisation, record and turn in a song. 


\section{Emacs and Org-Mode for Organization and Note Taking}
\label{sec:orga38c465}
\subsection{Capture}
\label{sec:org9c35493}
\subsubsection{Capture notes in sub-sections.}
\label{sec:org42de4d6}
\subsubsection{Capture in correct place.}
\label{sec:org77a37b6}
\subsection{Organize}
\label{sec:org0fbd7c7}
\subsubsection{Provide a clear outline of notes}
\label{sec:org57c94a8}
\subsubsection{File the topics or notes into correct place, with a link}
\label{sec:orgdd8ad02}
\subsection{Publish}
\label{sec:org76327a0}
\subsubsection{As a webpage that can be browsed in github.}
\label{sec:org6d9707b}
\subsubsection{Latex formatting}
\label{sec:org5ee0f8c}

\section{Example / Blogs}
\label{sec:org8177f08}
\subsection{Refiling and Organizing Notes}
\label{sec:orgb86d10b}
\begin{itemize}
\item \url{https://mollermara.com/blog/Fast-refiling-in-org-mode-with-hydras/}
\item 
\end{itemize}


\section{[1/3] Org-Mode Todos}
\label{sec:org3ed8bfe}
\subsection{{\bfseries\sffamily DONE} Enable indent mode in orgmode by default}
\label{sec:org75c25eb}
\subsection{{\bfseries\sffamily TODO} Create a task list to track what needs to be done.}
\label{sec:org83602f0}
\subsection{{\bfseries\sffamily TODO} Create templates, reuse once you have a few filled in.}
\label{sec:orgcec521c}


\section{[0/5] Directory Structure}
\label{sec:org7373373}
\subsection{{\bfseries\sffamily TODO} Set this up and then fill in the details. Get the infrastructure together.}
\label{sec:org79900ce}
\subsection{{\bfseries\sffamily TODO} Where does code repo sit?}
\label{sec:orgf133540}
\subsection{{\bfseries\sffamily TODO} Add links to the structure below.}
\label{sec:org5d64f8a}
\subsection{{\bfseries\sffamily TODO} Create functions, keep it simple.}
\label{sec:org6d336a9}
\subsection{{\bfseries\sffamily TODO} Where to put books?}
\label{sec:org16971cb}

\section{[0/4] Publishing}
\label{sec:org827e4be}
\subsection{{\bfseries\sffamily TODO} Check into GIT and publish.}
\label{sec:org7535606}
\subsection{{\bfseries\sffamily TODO} Publish only one website.}
\label{sec:org34fc760}
\subsection{{\bfseries\sffamily TODO} Update .emacs to handle structure/publishing}
\label{sec:org926cfec}
\subsection{{\bfseries\sffamily TODO} Make Orgmode Publishing cleaner}
\label{sec:org72e6c5e}
\begin{itemize}
\item \url{http://www.personal.psu.edu/nus173/sitecreation.html}
\item \url{https://github.com/cinsk/jekyll-org/}
\item \url{https://jgkamat.github.io/blog/website1.html}
\item \url{https://orgmode.org/worg/org-tutorials/org-publish-html-tutorial.html}
\end{itemize}

\section{Compute}
\label{sec:orga68d835}
\subsection{{\bfseries\sffamily TODO} Setup AWS for processing}
\label{sec:orgc35f107}

\section{[1/7] Emacs}
\label{sec:org518566c}
\subsection{{\bfseries\sffamily IN-PROGRESS} Setup Python IDE}
\label{sec:orgbb0e2d5}
\subsection{{\bfseries\sffamily IN-PROGRESS} Setup C++ IDE}
\label{sec:org80a08ee}
\subsection{{\bfseries\sffamily DONE} Find a good theme}
\label{sec:org96c18c8}
\subsection{{\bfseries\sffamily TODO} Get emacs to recognize file paths and open them}
\label{sec:org3919c67}
\subsection{{\bfseries\sffamily IN-PROGRESS} Enable CUA mode}
\label{sec:org97df42f}
\subsection{{\bfseries\sffamily TODO} Find a better parenthesis matcher}
\label{sec:org2e20f50}
\subsection{{\bfseries\sffamily TODO} Buffer list and file browser}
\label{sec:orgc2595f8}

\section{[0/1] Interesting Stuff}
\label{sec:org598614b}
\subsection{{\bfseries\sffamily TODO} Python to Verilog/C++ Verification type setup}
\label{sec:orge25d46e}

\section{Topic}
\label{sec:orgdf1b2ba}
Has the major subjects inside. 2
Raw Notes is one main file, that is then manually refiled

\section{Subtopic}
\label{sec:orgef29ed5}
\begin{itemize}
\item Theory (includes formulation as well as code to play with)
\item Code or Application
\item Resources and References
\end{itemize}


\section{Mathematics}
\label{sec:org6079cb4}
\subsection{Linear Algebra}
\label{sec:org748cb2f}
\subsubsection{Subtopics}
\label{sec:org62d8f38}
\subsection{Calculus}
\label{sec:orgd8a65f6}
\subsubsection{Subtopics}
\label{sec:org6bbb145}
\subsection{Probability and Statistics}
\label{sec:orgc948b18}
\subsubsection{Subtopics}
\label{sec:org8b499a5}
\section{Machine Learning / Artificial Intelligence}
\label{sec:orgfc3c5a2}
\subsection{Data Analysis}
\label{sec:orgb22d9c5}
\subsubsection{Categorical and Continuous Features}
\label{sec:orgfa33216}
\subsection{Model Development}
\label{sec:org629f7f2}
\subsubsection{Linear Regression}
\label{sec:org22c2fd6}
\subsubsection{Logisitic Regression}
\label{sec:org07ea41a}
\subsubsection{K-Nearest Neighbor}
\label{sec:org2346001}
\subsubsection{Deep Neural Networks}
\label{sec:orgf23d4b6}
\subsubsection{Support Vector Machines}
\label{sec:orgec48aee}
\subsection{Optimization Algorithms}
\label{sec:orgea54795}
\subsubsection{Learning Rate Intuition}
\label{sec:org57eb424}
\subsubsection{Normal Equations}
\label{sec:org501cdde}
\subsubsection{Gradient Descent}
\label{sec:orge8706c1}
\begin{itemize}
\item Batch Gradient Descent
\item Stochastic Gradient Descent
\item COnjugate Gradient Descent
\end{itemize}
\subsubsection{BGFS / L-BGFS}
\label{sec:org6d566c3}
\subsection{Loss / Accuracy Measurements}
\label{sec:org896c7f7}
\subsection{Applications}
\label{sec:org6e1ad39}
\subsubsection{Kaggle}
\label{sec:orgf7c7225}
\begin{enumerate}
\item Competitions
\label{sec:org1a7e6d2}
\end{enumerate}
\section{Digital Design}
\label{sec:org78338d1}
\subsection{Digital Design Flow}
\label{sec:org5ced34d}
\section{Computer Architecture}
\label{sec:org11e48fb}
\section{Music}
\label{sec:org6c9a902}
\subsection{Theory}
\label{sec:org752451f}
\subsubsection{Subtopic}
\label{sec:orgf0210b5}
\subsection{Application}
\label{sec:org11c723b}
\section{Audio DSP}
\label{sec:org933b0c2}
\subsection{Theory}
\label{sec:orged38cc0}
\subsubsection{Subtopic}
\label{sec:org62de67e}
\subsection{Application}
\label{sec:orgd47371c}
\section{Code}
\label{sec:org5d7eb54}
\subsection{Python}
\label{sec:orgfaead74}
\subsection{Cpp}
\label{sec:orge6c6819}



\section{Notes}
\label{sec:org302f8d8}
Coding is done with each topics.
\subsection{{\bfseries\sffamily IN-PROGRESS} Need to figure out how to handle code from different directories.}
\label{sec:org48483bb}
\end{document}
