% Created 2018-02-14 Wed 10:25
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{tikz}
\author{Monib Ahmed}
\date{\today}
\title{}
\hypersetup{
 pdfauthor={Monib Ahmed},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 25.3.1 (Org mode 9.1.5)}, 
 pdflang={English}}
\begin{document}

\tableofcontents

\section{Bayesian Learning}
\label{sec:org3f147b4}
Bayesian learning is a type of A/B learning algorithm
\subsection{Bayes Rules and Probability Review}
\label{sec:org00782f5}
\subsubsection{Undergraduate level probability}
\label{sec:orgdf81f5d}
\begin{itemize}
\item Discrete and Continuous Distributions
\item Joint Distributions
\item Conditional Distributions
\item PDF, PMF, CDF
\end{itemize}
\subsection{Traditional A/B Testing}
\label{sec:org1653e68}
\subsection{Bayesian A/B Testing}
\label{sec:org7370af2}

\section{Probability Review}
\label{sec:org597c699}
\subsection{Conditional Probability}
\label{sec:org3149781}
Conditional probability is a measure of the probability of an event
given that (by assumption, presumption, assertion or evidence) another
event has occured. 

The probability \(P(A|B)\) may or may nnot be equal to \(P(A)\). If
\(P(A|B) = P(A)\), then the events A and B are said to be
independent. In other words, having knowledge about either event does
not change our knowledge about the other event.

The probability \(P(A|B)\) is not equal to \(P(B|A)\). This relates to
sensitivty and specificity.

Conditional probability will sum to 1 for each branch, this is because
the space of random variables decreases. We are given something
happened, and this means that that probabiity is now '1'. 

\subsection{Joint Probability}
\label{sec:org723dfdd}
As the total number of possibilities grow, joint probabilities values
decrease exponentially. Computer have finite precision 32/64 bit. The
sum of all possible outcomes must equal 1. 

Eventually the computer will round down to 0, underflow. We can use
log probability instead. 

\subsection{Independence}
\label{sec:orgb58a3fd}
When two variables are independent, the joint becomes the multiple of
the marginals:

$$ P(A,B) = P(A)P(B)-P(A,B) $$

In this case if \(P(A,B)\) is zero, then the variables are indepedent. 

\subsection{Sensitivity and Specificity}
\label{sec:org228288b}
Sensitivity - probability of correct positive detection
Specificity - probability of correct negative detection

Sensitivity is the extent which true positives are not missed or
overlooked. 


Terminology:
\begin{center}
\begin{tabular}{ll}
Terminology & Description\\
\hline
P & Num of. Positive samples\\
N & Num of. Negative samples\\
TP & Num of. Positive hit samples (got right)\\
TN & Num of. Negative hit samples (got right)\\
FP & Num of. False Positives (false alarms)\\
FN & Num of. False Negatives (misses)\\
 & \\
\end{tabular}
\end{center}


Equations:
\begin{center}
\begin{tabular}{lll}
Equation & Description & Description\\
\hline
\(TPR = \frac{TP}{TP+FN}\) & Hit Rate, Sensitivity & hits\\
\(TNR = \frac{TN}{TN+FP}\) & Specificity & misses\\
\(PPV = \frac{TP}{TP+FP}\) & Precision & \\
\(NPV = \frac{TN}{TN+FN}\) &  & \\
\end{tabular}
\end{center}

\section{Bayes Rule}
\label{sec:org0c3ae02}

Bayes' theorem describes the probability of an event, based on prior
knowledge of conditions that might be related to an event. One
application of Bayes Theorem is Bayesian inference. 

In probability theory, an event is a set of outcomes of an experiment
(a subset of the sample space) to which a probability is assigned. A
single outcome may be an element of many different events and
different events may not be equally likely. An event defines a
complementary event (the event not occuring), and together these
define a Bernouli trial (did the event occur or not?). 

The sample space is finite, and any subset sample space is an
event. However this does not work in cases where the sample space is
infinite. 

Defining all subsets of the sample space as events works well when
there are only finitely many outcomes, but gives problems when the
sample space is infinite. 

For the standard tools of probability theory, such as joint and
conditional probabilities, to work, it is necessary to use
\(\sigma\)-Algebra (a familt closed under complementation and countable
unions of its members). 

Bayes' theorem is stated mathematically as the following equation: 
$$P(A|B) = \frac{P(B|A)P(A)}{P(B)}$$

\(P(A|B)\) is a conditional probability, the likelihood of event A
occuring given the B is true.  

\(P(B|A)\) is a conditional probability, the likelihood of event B
occuring given the A is true.  

\(P(A)\) and \(P(B)\) are the probabilities of observing A and B
independently of each other (marginal probability).

\subsection{Bayes Theorem Manipulation}
\label{sec:orgcfd49f4}
Bayes Theorem essentially says that the events going forward is
equivalent to the events going backwards. 

This is shown:
$$P(A|B) = \frac{P(A,B)}{P(B)}$$
$$P(B|A) = \frac{P(B,A)}{P(A)}$$
$$P(A,B) = P(B,A)             $$
$$P(A|B)P(B) = P(B|A)P(A)     $$

\subsection{Gamblers Fallacy}
\label{sec:org80df7fa}
The belief that things will "even out" in the end. If you've just lost
100 times, then you have a better chance of winning. This assumption
is incorrect, all events are independent. It doesn't matter how many
times you've lost alredy, your chances of losing next are the same. 

\subsection{Monty Hall Problem}
\label{sec:orgd48d985}
Three doors, one with a car behind it. You are asked to choose a door, 

Stick with your choice, then on the last choice, switch.

\begin{latex}


\tikzstyle{level 1}=[level distance=3.5cm, sibling distance=3.5cm]
\tikzstyle{level 2}=[level distance=3.5cm, sibling distance=2cm]

\tikzstyle{bag} = [text width=4em, text centered]
\tikzstyle{end} = [circle, minimum width=3pt,fill, inner sep=0pt]

\begin{tikzpicture}[grow=right, sloped]
\node[bag] {Bag 1 $4W, 3B$}
    child {
        node[bag] {Bag 2 $4W, 5B$}        
            child {
                node[end, label=right:
                    {$P(W_1\cap W_2)=\frac{4}{7}\cdot\frac{4}{9}$}] {}
                edge from parent
                node[above] {$W$}
                node[below]  {$\frac{4}{9}$}
            }
            child {
                node[end, label=right:
                    {$P(W_1\cap B_2)=\frac{4}{7}\cdot\frac{5}{9}$}] {}
                edge from parent
                node[above] {$B$}
                node[below]  {$\frac{5}{9}$}
            }
            edge from parent 
            node[above] {$W$}
            node[below]  {$\frac{4}{7}$}
    }
    child {
        node[bag] {Bag 2 $3W, 6B$}        
        child {
                node[end, label=right:
                    {$P(B_1\cap W_2)=\frac{3}{7}\cdot\frac{3}{9}$}] {}
                edge from parent
                node[above] {$B$}
                node[below]  {$\frac{3}{9}$}
            }
            child {
                node[end, label=right:
                    {$P(B_1\cap B_2)=\frac{3}{7}\cdot\frac{6}{9}$}] {}
                edge from parent
                node[above] {$W$}
                node[below]  {$\frac{6}{9}$}
            }
        edge from parent         
            node[above] {$B$}
            node[below]  {$\frac{3}{7}$}
    };
\end{tikzpicture}
\end{latex}

\section{References}
\label{sec:orgde29740}
\begin{itemize}
\item Events: \url{https://en.wikipedia.org/wiki/Event\_(probability\_theory)}
\item Condition probability: \url{https://en.wikipedia.org/wiki/Conditional\_probability}
\item Sensitivity and Specificity:
\url{https://en.wikipedia.org/wiki/Sensitivity\_and\_specificity}
\item \(\sigma\)-Algebra: \url{https://en.wikipedia.org/wiki/Sigma-algebra}
\item Confusion Matrix:
\url{https://en.wikipedia.org/wiki/Sensitivity\_and\_specificity}
\item Monty Hall Problem: \url{http://mathworld.wolfram.com/MontyHallProblem.html}
\end{itemize}
\end{document}
